Access to Food in Chicago: \\ a Hierarchical Perspective

### 2016-11-21 paper.tex
lots of changes whoops

\documentclass{IEEEtran}

@@

\section{Introduction}
Access to readily available and inexpensive healthy food options is important for personal health. Unfortunately, for some in society today, access is not equitable. Some towns and neighborhoods have excellent healthy food options. Others do not. In some locations it is difficult to impossible for many residents to find healthy food options. In these areas, known as food deserts, there is readily available processed, calorie dense but nutrient poor foods.

@@

\subsection{Food Deserts}
There is no single agreed upon definition of a food desert. Some common metrics are based on distances to nearest supermarket with cutoffs at 1 mile for urban areas and 10 miles for rural areas. 1 mile may seem like a short distance to travel, but in urban areas with low car ownership rates where residents rely on public transportation, a 1 mile journey can take a substantial amount of time. 
% TODO: insert citation
For this work we used the definition from %TODO: citation
of defining a city block as being in a food desert if the city block is more than 1 mile from a supermarket. Supermarket in this context is a grocery store that is larger than 10000 square feet %TODO: citation
that is not primarily a liquor store. Distance is defined as the great circle distance from the center of mass of the city block to the center of mass of the grocery store.

\section{Methods}
In the following section we describe the procedures used. We begin by describing the data used and including data sources. Then we move on to describing the types of models used.

\subsection{Data Gathering and Manipulation}

@@

\subsubsection{Block level data}

\paragraph{ Crimes 2001 - present}
This file contains a record for crimes in Chicago since 2001 with information about the type of crime as well as its location. The location is pseudo-anonymized to be random but within the same city block. For each city block we counted the total number of crimes committed within 1 mile in 2009. Our hypothesis \textit{a priori} was that food deserts were often located in high-crime areas.

@@

\paragraph{ CTA Ridership: Avg. Weekly Boardings during October 2010}
This file contains average weekly boardings for the month of October 2010 for every bus stop in Chicago. We counted the total boardings for all stops within a mile of each city block. Our hypothesis was that residents of food deserts would tend to have a higher reliance on public transportation than residents in other areas.

@@

\subsubsection{Neighborhood level data}

@@

\paragraph{ Race by Community Area }
This file contains a record for every neighborhood in Chicago with the number of residents of each race who reside in that neighborhood.

\subsection{Generalized Linear Models}

@@

\subsection{Hierarchical Models}

Hierarchical models are another extension to the family of linear models which allow for

\subsection{Models Fit}

\subsubsection{Complete Pooling}

@@

\subsubsection{No Pooling}

@@

\subsubsection{Partial pooling}

@@

\subsubsection{Hierarchical}

@@

\subsection{Model Comparison}

Models were compared using AIC and cross validated Breir Score (Mean Square Error in the case of 2-class logistic regression)

\section{Results}

\subsection{Model Parameters}

\subsubsection{No Pooling}

\subsubsection{Complete Pooling}

\subsubsection{Partial Pooling}

\subsubsection{Hierarchical}

\section{Conclusions}

>>>>

\documentclass{report}

\usepackage[margin=1in]{geometry}

@@

\section*{Introduction}
Access to readily available and inexpensive healthy food options is important for personal health. Unfortunately, for some in society today, access is not equitable. Some towns and neighborhoods have excellent healthy food options. Others do not. In some locations it is difficult to impossible for many residents to find healthy food options. In these areas, known as food deserts, there is readily available processed, calorie dense but nutrient poor foods.

@@

\subsection*{Food Deserts}
There is no single agreed upon definition of a food desert. Some common metrics are based on distances to nearest supermarket with cutoffs at 1 mile for urban areas and 10 miles for rural areas. 1 mile may seem like a short distance to travel, but in urban areas with low car ownership rates where residents rely on public transportation, a 1 mile journey can take a substantial amount of time. 
% TODO: insert citation
For this work we used the definition from %TODO: citation
of defining a city block as being in a food desert if the city block is more than 1 mile from a supermarket. Supermarket in this context is a grocery store that is larger than 10000 square feet %TODO: citation
that is not primarily a liquor store. Distance is defined as the great circle distance from the center of mass of the city block to the center of mass of the grocery store.

\section*{Methods}
In the following section we describe the procedures used. We begin by describing the data used and including data sources. Then we move on to describing the types of models used.

\subsection*{Data Gathering and Manipulation}

@@

\subsubsection*{Block level data}

% \paragraph{ Crimes 2001 - present}
% This file contains a record for crimes in Chicago since 2001 with information about the type of crime as well as its location. The location is pseudo-anonymized to be random but within the same city block. For each city block we counted the total number of crimes committed within 1 mile in 2009. Our hypothesis \textit{a priori} was that food deserts were often located in high-crime areas.

@@

\paragraph{ CTA Ridership: Avg. Weekly Boardings during October 2010}
This file contains average weekly boardings for the month of October 2010 for every CTA (Chicago Transit Authority) bus stop in Chicago. We counted the total boardings for all stops within a mile of each city block. Our hypothesis was that residents of food deserts would tend to have a higher reliance on public transportation than residents in other areas.

@@

\subsubsection*{Neighborhood level data}

@@

\paragraph{ Race by Community Area }
This file contains a record for every neighborhood in Chicago with the number of residents of each race who reside in that neighborhood. \\

We tried to gather data on crimes and use that information in the model, however the available dataset for crimes in chicago is rather large ($>$1 GB) and we didn't have time to finish extracting features from that model. We hypothesized that food deserts were more likely to be in high crime areas.

\subsection*{Generalized Linear Models}

@@

\subsection*{Mixed Models}

So far we have discussed models which have only ``fixed effects'', that is, effects that are nonrandom and do not vary across covariates. We may believe for example that each neighborhood is different enough to merit its own intercept but that each neighborhood is sampled from a large population of candidate neighborhoods. In that situation we're not interested necessarily in each intercept, but more the variability between neighborhoods. In this situation we would fit a random intercept model where each intercept is (without loss of generality) distributed normally with mean zero and variance $\sigma^2_\alpha$.  To further generalize, we could allow the fixed effect coefficients to vary in a similar manner. This is called a random slope model. In our case we fit random intercept models with fixed effects for each slope. This reflects our belief that the neighborhoods are different from each other and should have different baseline probabilities of being a food desert (due to potentially unmeasured covariates) but that the effect of CTA ridership and number of vacant buildings nearby should be the same across all neighborhoods.

\subsection*{Hierarchical Models}

Hierarchical models are another extension to the family of linear models which allow for hierarchical structured data. Recalling the random intercept model, since we have neighborhood level covariates, we would like to use the information contained within to predict the random intercept for each neighborhood. 
\subsection*{Models Fit}

\subsubsection*{Complete Pooling}

@@

\subsubsection*{No Pooling}

@@

\subsubsection*{Partial pooling}

@@

\subsubsection*{Hierarchical}

@@

\subsection*{Model Comparison}

Models were compared using AIC and cross validated Breir Score (Mean Square Error in the case of 2-class logistic regression).

\section*{Results}

\subsection*{Model Parameters}

\subsubsection*{Complete Pooling}

% % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% % Date and time: Mon, Nov 21, 2016 - 10:52:26
% \begin{table}[!htbp] \centering 
%   \caption{Complete pooling model summary} 
%   \label{cpresult} 
% \begin{tabular}{@{\extracolsep{5pt}}lc} 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex] 
%  & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
% \cline{2-2} 
% \\[-1.8ex] & desert \\ 
% \hline \\[-1.8ex] 
%  CTA\_counts & $-$1.585$^{***}$ (0.040) \\ 
%   & \\ 
%  vacant\_counts & 0.411$^{***}$ (0.018) \\ 
%   & \\ 
%  Constant & $-$2.848$^{***}$ (0.028) \\ 
%   & \\ 
% \hline \\[-1.8ex] 
% Observations & 36,870 \\ 
% Log Likelihood & $-$9,913.778 \\ 
% Akaike Inf. Crit. & 19,833.560 \\ 
% \hline 
% \hline \\[-1.8ex] 
% \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
% \end{tabular} 
% \end{table}

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Nov 21, 2016 - 13:53:33
\begin{table}[!htbp] \centering 
  \caption{Complete pooling model summary} 
  \label{cpresult} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & desert \\ 
\hline \\[-1.8ex] 
 CTA\_counts & $-$1.588$^{***}$ (0.040) \\ 
 vacant\_counts & 0.410$^{***}$ (0.018) \\ 
 crime & 0.056$^{***}$ (0.019) \\ 
 Constant & $-$2.849$^{***}$ (0.029) \\ 
\hline \\[-1.8ex] 
Observations & 36,870 \\ 
Log Likelihood & $-$9,909.356 \\ 
Akaike Inf. Crit. & 19,826.710 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\subsubsection*{No Pooling}

% % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% % Date and time: Mon, Nov 21, 2016 - 10:52:50
% \begin{table}[!htbp] \centering 
%   \caption{No pooling model summary} 
%   \label{npresult} 
% \begin{tabular}{@{\extracolsep{5pt}}lc} 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex] 
%  & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
% \cline{2-2} 
% \\[-1.8ex] & desert \\ 
% \hline \\[-1.8ex] 
%  CTA\_counts & $-$0.783$^{***}$ (0.061) \\ 
%  vacant\_counts & $-$0.408$^{***}$ (0.038) \\ 
%  NeighborhoodArcher Heights & $-$0.379 (1,446.793) \\ 
%  NeighborhoodArmour Square & 17.949 (757.683) \\ 
%  NeighborhoodAshburn & 18.311 (757.683) \\ 
%  NeighborhoodAuburn Gresham & 14.135 (757.683) \\ 
%  NeighborhoodAustin & 16.948 (757.683) \\ 
%  NeighborhoodAvalon Park & 16.015 (757.683) \\ 
%  NeighborhoodAvondale & 0.466 (1,120.896) \\ 
%  NeighborhoodBelmont Cragin & $-$0.232 (951.136) \\ 
%  NeighborhoodBeverly & 16.982 (757.683) \\ 
%  NeighborhoodBridgeport & 16.182 (757.683) \\ 
%  NeighborhoodBrighton Park & $-$0.294 (1,090.129) \\ 
%  NeighborhoodBurnside & $-$0.020 (2,106.584) \\ 
%  NeighborhoodCalumet Heights & 15.497 (757.683) \\ 
%  NeighborhoodChatham & 17.624 (757.683) \\ 
%  NeighborhoodChicago Lawn & 17.597 (757.683) \\ 
%  NeighborhoodClearing & 20.147 (757.683) \\ 
%  NeighborhoodDouglas & 0.264 (1,789.225) \\ 
%  NeighborhoodDunning & 18.404 (757.683) \\ 
%  NeighborhoodEast Side & $-$0.950 (1,160.930) \\ 
%  NeighborhoodEdgewater & 0.290 (1,092.033) \\ 
%  NeighborhoodEdison Park & 16.367 (757.683) \\ 
%  NeighborhoodEnglewood & 19.683 (757.683) \\ 
%  NeighborhoodForest Glen & 17.800 (757.683) \\ 
%  NeighborhoodFuller Park & 18.461 (757.683) \\ 
%  NeighborhoodGage Park & $-$0.038 (1,116.702) \\ 
%  NeighborhoodGarfield Park & 20.416 (757.683) \\ 
%  NeighborhoodGarfield Ridge & 18.375 (757.683) \\ 
%  NeighborhoodGrand Boulevard & 18.233 (757.683) \\ 
%  NeighborhoodGreater Grand Crossing & 1.174 (1,060.103) \\ 
%  NeighborhoodHegewisch & 22.019 (757.683) \\ 
%  NeighborhoodHermosa & $-$0.097 (1,318.741) \\ 
%  NeighborhoodHumboldt Park & 14.379 (757.683) \\ 
%  NeighborhoodHyde Park & 0.320 (1,585.606) \\ 
%  NeighborhoodIrving Park & $-$0.045 (1,000.878) \\ 
%  NeighborhoodJefferson Park & $-$0.628 (1,084.084) \\ 
%  NeighborhoodKenwood & 0.139 (1,833.318) \\ 
%  NeighborhoodLake View & 0.553 (997.500) \\ 
%  NeighborhoodLincoln Park & 0.295 (1,091.797) \\ 
%  NeighborhoodLincoln Square & 0.151 (1,086.733) \\ 
%  NeighborhoodLogan Square & 0.368 (928.968) \\ 
%  NeighborhoodLoop & 4.566 (1,622.709) \\ 
%  NeighborhoodLower West Side & $-$0.194 (1,142.009) \\ 
%  NeighborhoodMcKinley Park & $-$0.442 (1,387.487) \\ 
%  NeighborhoodMontclaire & $-$0.641 (1,429.041) \\ 
%  NeighborhoodMorgan Park & 14.297 (757.683) \\ 
%  NeighborhoodMount Greenwood & $-$1.030 (1,241.482) \\ 
%  NeighborhoodNear North Side & 1.297 (1,065.341) \\ 
%  NeighborhoodNear South Side & 0.223 (1,645.912) \\ 
%  NeighborhoodNear West Side & 19.805 (757.683) \\ 
%  NeighborhoodNew City & 17.535 (757.683) \\ 
%  NeighborhoodNorth Center & 0.027 (1,073.236) \\ 
%  NeighborhoodNorth Lawndale & 20.141 (757.683) \\ 
%  NeighborhoodNorth Park & $-$0.525 (1,315.485) \\ 
%  NeighborhoodNorwood Park & 15.844 (757.683) \\ 
%  NeighborhoodO'Hare & 17.370 (757.683) \\ 
%  NeighborhoodOakland & $-$0.346 (2,337.413) \\ 
%  NeighborhoodPortage Park & 17.008 (757.683) \\ 
%  NeighborhoodPullman & 20.484 (757.683) \\ 
%  NeighborhoodRiverdale & $-$0.904 (2,643.084) \\ 
%  NeighborhoodRogers Park & $-$0.162 (1,141.035) \\ 
%  NeighborhoodRoseland & 21.120 (757.683) \\ 
%  NeighborhoodSouth Chicago & 0.467 (1,066.990) \\ 
%  NeighborhoodSouth Deering & 18.453 (757.683) \\ 
%  NeighborhoodSouth Lawndale & $-$0.081 (1,038.677) \\ 
%  NeighborhoodSouth Shore & 14.922 (757.683) \\ 
%  NeighborhoodUptown & 0.818 (1,290.791) \\ 
%  NeighborhoodWashington Heights & 17.330 (757.683) \\ 
%  NeighborhoodWashington Park & 19.825 (757.683) \\ 
%  NeighborhoodWest Elsdon & $-$0.351 (1,288.127) \\ 
%  NeighborhoodWest Lawn & 18.052 (757.683) \\ 
%  NeighborhoodWest Pullman & 20.407 (757.683) \\ 
%  NeighborhoodWest Ridge & 18.432 (757.683) \\ 
%  NeighborhoodWest Town & 0.557 (941.762) \\ 
%  NeighborhoodWoodlawn & 17.453 (757.683) \\ 
%  Constant & $-$20.670 (757.683) \\ 
% \hline \\[-1.8ex] 
% Observations & 36,870 \\ 
% Log Likelihood & $-$6,416.746 \\ 
% Akaike Inf. Crit. & 12,987.490 \\ 
% \hline 
% \hline \\[-1.8ex] 
% \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
% \end{tabular} 
% \end{table}

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Nov 21, 2016 - 13:54:08
\begin{table}[!htbp] \centering 
  \caption{No pooling model summary} 
  \label{npresult} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & desert \\ 
\hline \\[-1.8ex] 
 CTA\_counts & $-$0.783$^{***}$ (0.061) \\ 
 vacant\_counts & $-$0.408$^{***}$ (0.038) \\ 
 crime & 0.101$^{***}$ (0.023) \\ 
 NeighborhoodArcher Heights & $-$0.375 (1,446.209) \\ 
 NeighborhoodArmour Square & 17.931 (757.423) \\ 
 NeighborhoodAshburn & 18.317 (757.423) \\ 
 NeighborhoodAuburn Gresham & 14.142 (757.423) \\ 
 NeighborhoodAustin & 16.954 (757.423) \\ 
 NeighborhoodAvalon Park & 16.000 (757.423) \\ 
 NeighborhoodAvondale & 0.474 (1,120.121) \\ 
 NeighborhoodBelmont Cragin & $-$0.218 (950.607) \\ 
 NeighborhoodBeverly & 17.015 (757.423) \\ 
 NeighborhoodBridgeport & 16.189 (757.423) \\ 
 NeighborhoodBrighton Park & $-$0.312 (1,089.199) \\ 
 NeighborhoodBurnside & $-$0.026 (2,105.039) \\ 
 NeighborhoodCalumet Heights & 15.508 (757.423) \\ 
 NeighborhoodChatham & 17.625 (757.423) \\ 
 NeighborhoodChicago Lawn & 17.574 (757.423) \\ 
 NeighborhoodClearing & 20.174 (757.423) \\ 
 NeighborhoodDouglas & 0.258 (1,787.332) \\ 
 NeighborhoodDunning & 18.424 (757.423) \\ 
 NeighborhoodEast Side & $-$0.936 (1,160.353) \\ 
 NeighborhoodEdgewater & 0.313 (1,091.423) \\ 
 NeighborhoodEdison Park & 16.364 (757.423) \\ 
 NeighborhoodEnglewood & 19.671 (757.423) \\ 
 NeighborhoodForest Glen & 17.814 (757.423) \\ 
 NeighborhoodFuller Park & 18.528 (757.423) \\ 
 NeighborhoodGage Park & $-$0.006 (1,115.834) \\ 
 NeighborhoodGarfield Park & 20.438 (757.423) \\ 
 NeighborhoodGarfield Ridge & 18.394 (757.423) \\ 
 NeighborhoodGrand Boulevard & 18.242 (757.423) \\ 
 NeighborhoodGreater Grand Crossing & 1.179 (1,059.845) \\ 
 NeighborhoodHegewisch & 22.005 (757.423) \\ 
 NeighborhoodHermosa & $-$0.076 (1,317.960) \\ 
 NeighborhoodHumboldt Park & 14.370 (757.423) \\ 
 NeighborhoodHyde Park & 0.316 (1,584.758) \\ 
 NeighborhoodIrving Park & $-$0.052 (1,000.494) \\ 
 NeighborhoodJefferson Park & $-$0.612 (1,083.140) \\ 
 NeighborhoodKenwood & 0.162 (1,831.358) \\ 
 NeighborhoodLake View & 0.573 (996.840) \\ 
 NeighborhoodLincoln Park & 0.284 (1,090.999) \\ 
 NeighborhoodLincoln Square & 0.152 (1,086.535) \\ 
 NeighborhoodLogan Square & 0.374 (928.612) \\ 
 NeighborhoodLoop & 4.593 (1,627.447) \\ 
 NeighborhoodLower West Side & $-$0.179 (1,141.349) \\ 
 NeighborhoodMcKinley Park & $-$0.425 (1,386.519) \\ 
 NeighborhoodMontclaire & $-$0.665 (1,428.421) \\ 
 NeighborhoodMorgan Park & 14.296 (757.423) \\ 
 NeighborhoodMount Greenwood & $-$1.035 (1,240.962) \\ 
 NeighborhoodNear North Side & 1.286 (1,065.410) \\ 
 NeighborhoodNear South Side & 0.203 (1,644.854) \\ 
 NeighborhoodNear West Side & 19.807 (757.423) \\ 
 NeighborhoodNew City & 17.533 (757.423) \\ 
 NeighborhoodNorth Center & 0.025 (1,072.777) \\ 
 NeighborhoodNorth Lawndale & 20.140 (757.423) \\ 
 NeighborhoodNorth Park & $-$0.485 (1,314.011) \\ 
 NeighborhoodNorwood Park & 15.859 (757.423) \\ 
 NeighborhoodO'Hare & 17.366 (757.423) \\ 
 NeighborhoodOakland & $-$0.333 (2,335.785) \\ 
 NeighborhoodPortage Park & 17.004 (757.423) \\ 
 NeighborhoodPullman & 20.484 (757.423) \\ 
 NeighborhoodRiverdale & $-$0.950 (2,642.673) \\ 
 NeighborhoodRogers Park & $-$0.180 (1,140.236) \\ 
 NeighborhoodRoseland & 21.135 (757.423) \\ 
 NeighborhoodSouth Chicago & 0.471 (1,066.274) \\ 
 NeighborhoodSouth Deering & 18.462 (757.423) \\ 
 NeighborhoodSouth Lawndale & $-$0.066 (1,038.034) \\ 
 NeighborhoodSouth Shore & 14.902 (757.423) \\ 
 NeighborhoodUptown & 0.845 (1,290.142) \\ 
 NeighborhoodWashington Heights & 17.343 (757.423) \\ 
 NeighborhoodWashington Park & 19.848 (757.423) \\ 
 NeighborhoodWest Elsdon & $-$0.357 (1,287.354) \\ 
 NeighborhoodWest Lawn & 18.031 (757.423) \\ 
 NeighborhoodWest Pullman & 20.427 (757.423) \\ 
 NeighborhoodWest Ridge & 18.428 (757.423) \\ 
 NeighborhoodWest Town & 0.566 (941.296) \\ 
 NeighborhoodWoodlawn & 17.508 (757.423) \\ 
 Constant & $-$20.678 (757.423) \\ 
\hline \\[-1.8ex] 
Observations & 36,870 \\ 
Log Likelihood & $-$6,407.134 \\ 
Akaike Inf. Crit. & 12,970.270 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\subsubsection*{Partial Pooling}

% % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% % Date and time: Mon, Nov 21, 2016 - 10:50:32
% \begin{table}[!htbp] \centering 
%   \caption{Partial pooling model summary} 
%   \label{ppresult} 
% \begin{tabular}{@{\extracolsep{5pt}}lc} 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex] 
%  & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
% \cline{2-2} 
% \\[-1.8ex] & desert \\ 
% \hline \\[-1.8ex] 
%  CTA\_counts & $-$0.794$^{***}$ (0.061) \\
%   & \\ 
%  vacant\_counts & $-$0.403$^{***}$ (0.038) \\ 
%   & \\ 
%  Constant & $-$6.300$^{***}$  (0.657) \\ 
%   & \\ 
% \hline \\[-1.8ex] 
% Observations & 36,870 \\ 
% Log Likelihood & $-$6,574.287 \\ 
% Akaike Inf. Crit. & 13,156.580 \\ 
% Bayesian Inf. Crit. & 13,190.640 \\ 
% \hline 
% \hline \\[-1.8ex] 
% \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
% \end{tabular} 
% \end{table}

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Nov 21, 2016 - 13:55:27
\begin{table}[!htbp] \centering 
  \caption{Partial pooling model summary} 
  \label{ppresult} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & desert \\ 
\hline \\[-1.8ex] 
 CTA\_counts & $-$0.794$^{***}$ (0.061) \\ 
 vacant\_counts & $-$0.404$^{***}$ (0.038) \\ 
 crime & 0.101$^{***}$ (0.023) \\ 
 Constant & $-$6.307$^{***}$ (0.657) \\ 
\hline \\[-1.8ex] 
Observations & 36,870 \\ 
Log Likelihood & $-$6,564.705 \\ 
Akaike Inf. Crit. & 13,139.410 \\ 
Bayesian Inf. Crit. & 13,181.990 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\subsubsection*{Hierarchical}

\section*{Conclusions}
